NHF1_FeatureRelativeFigureGeneration

### 2023-11-27 R/NHF1_FeatureRelativeDataGeneration.Rmd
Added analysis with updated nucleosome map
- The previous nucleosome map (hg19_mnase_all) was not well documented. The new nucleosome map (hg19_LCL_mnase_all_mappable) has much clearer documentation on its origins.
- This new map also has blacklisted regions removed, using Dr. Wyrick's intersect_MNasenucs_Blacklist.pl script and the DAC_Duke_hg19_excludable regions, which were also added to the new "perl" directory.
- R scripts were also altered slightly to remove whitespace, standardize spacing after commas, etc.
- Lastly, a bug was discovered and fixed in the figure S16 generation code. (5'

---
title: "NHF1_FeatureRelativeDataGeneration"
author: "Ben Morledge-Hampton"
date: "2023-07-18"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered, TG_filtered]
---

@@

cellType = "NHF1"
CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
mismatchTypes = list(`C>T_CC>TT` = NULL)
features = list(`CTCF_known1_DHS` = NULL, `CTCF_known1_non-DHS` = NULL, `hg19_mnase_all` = NULL)

@@

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", cellType)
mismatchesByReadDirectory = file.path(deaminationDataDirectory, "mismatches_by_read")
featureRelativeDataDirectory = file.path(deaminationDataDirectory,"feature_relative_analysis")
dir.create(featureRelativeDataDirectory, showWarnings = FALSE, recursive = TRUE)
```

@@

```{r generate_and_write_feature_relative_counts_data}
cpdFeatureRelativeData = copy(CPDTimepoints)
for (i in 1:length(cpdFeatureRelativeData)) {
  cpdFeatureRelativeData[[i]] = copy(mismatchTypes)
  for (j in 1:length(cpdFeatureRelativeData[[i]])) {
    cpdFeatureRelativeData[[i]][[j]] = copy(features)
    for (k in 1:length(cpdFeatureRelativeData[[i]][[j]])) {
      cpdFeatureRelativeData[[i]][[j]][[k]] = parseMismatchesByFeature(fread(
        generateFilePath(mismatchesByReadDirectory, dataTypeStrings$mismatchesByReadRelationFormatted, ".bed",
                         cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
                         timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
                         additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k],"_related"))
      ))

      fwrite(cpdFeatureRelativeData[[i]][[j]][[k]], sep = '\t', file = generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeData, ".tsv",
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
        additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k],"_related")
      ))

      fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = FEATURE_RELATIVE_POSITION,
                                      strandAlign = TRUE),
             sep = '\t', file = generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativePositionCounts, ".tsv",
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
        additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k],"_related")
      ))

      fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = FEATURE_RELATIVE_THREE_PRIME_CUT_SITE,
                                      strandAlign = TRUE),
             sep = '\t', file = generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeCutSiteCounts, ".tsv", strandPolarity = THREE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
        additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k],"_related")
      ))

      fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = FEATURE_RELATIVE_FIVE_PRIME_CUT_SITE,
                                      strandAlign = TRUE),
             sep = '\t', file = generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeCutSiteCounts, ".tsv", strandPolarity = FIVE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
        additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k],"_related")
      ))

      fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                                      strandAlign = TRUE),
             sep = '\t', file = generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = THREE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
        additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k],"_related")
      ))

      fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = MEAN_FIVE_PRIME_CUT_SITE_DISTANCE,
                                      strandAlign = TRUE),
             sep = '\t', file = generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = FIVE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
        additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k],"_related")
      ))

    }
  }
}

```

>>>>

---
title: "NHF1_FeatureRelativeDataGeneration"
author: "Ben Morledge-Hampton"
date: "2023-07-18"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: ~/bioinformatics
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects, ~/bioinformatics]
  filtering:
    label: "Filtering"
    value: TGG_filtered
    input: select
    choices: [NONE, TGG_filtered, TG_filtered]
---

@@

cellType = "NHF1"
CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
mismatchTypes = list(`C>T` = NULL, `CC>TT` = NULL, `C>T_CC>TT` = NULL)
# features = list(`CTCF_known1_DHS` = NULL, `CTCF_known1_non-DHS` = NULL,
#                 `hg19_mnase_all` = NULL, `hg19_LCL_mnase_all` = NULL, `hg19_LCL_mnase_all_mappable` = NULL)
features = list(`hg19_LCL_mnase_all_mappable_100bp` = NULL)

@@

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", cellType)
mismatchesByReadDirectory = file.path(deaminationDataDirectory, "mismatches_by_read")
featureRelativeDataDirectory = file.path(deaminationDataDirectory, "feature_relative_analysis")
dir.create(featureRelativeDataDirectory, showWarnings = FALSE, recursive = TRUE)
```

@@

```{r generate_and_write_feature_relative_counts_data}
cpdFeatureRelativeData = copy(CPDTimepoints)
for (i in 1:length(cpdFeatureRelativeData)) {
  cpdFeatureRelativeData[[i]] = copy(mismatchTypes)
  for (j in 1:length(cpdFeatureRelativeData[[i]])) {
    cpdFeatureRelativeData[[i]][[j]] = copy(features)
    for (k in 1:length(cpdFeatureRelativeData[[i]][[j]])) {
      cpdFeatureRelativeData[[i]][[j]][[k]] = parseMismatchesByFeature(fread(
        generateFilePath(mismatchesByReadDirectory, dataTypeStrings$mismatchesByReadRelationFormatted, ".bed",
                         cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
                         timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
                         additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k], "_related"))
      ))

      fwrite(cpdFeatureRelativeData[[i]][[j]][[k]], sep = '\t', file = generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeData, ".tsv",
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
        additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k], "_related")
      ))

      for (bool in c(TRUE, FALSE)) {

        if (bool) strandInfoText = "_strand_aligned" else strandInfoText = ""

        fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = FEATURE_RELATIVE_POSITION,
                                        strandAlign = bool),
               sep = '\t', na = "NA", file = generateFilePath(
          featureRelativeDataDirectory, dataTypeStrings$featureRelativePositionCounts, ".tsv",
          cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
          timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
          additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k], "_related", strandInfoText)
        ))

        fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = FEATURE_RELATIVE_THREE_PRIME_CUT_SITE,
                                        strandAlign = bool),
               sep = '\t', na = "NA", file = generateFilePath(
          featureRelativeDataDirectory, dataTypeStrings$featureRelativeCutSiteCounts, ".tsv", strandPolarity = THREE_PRIME,
          cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
          timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
          additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k], "_related", strandInfoText)
        ))

        fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = FEATURE_RELATIVE_FIVE_PRIME_CUT_SITE,
                                        strandAlign = bool),
               sep = '\t', na = "NA", file = generateFilePath(
          featureRelativeDataDirectory, dataTypeStrings$featureRelativeCutSiteCounts, ".tsv", strandPolarity = FIVE_PRIME,
          cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
          timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
          additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k], "_related", strandInfoText)
        ))

        fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                                        strandAlign = bool),
               sep = '\t', na = "NA", file = generateFilePath(
          featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = THREE_PRIME,
          cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
          timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
          additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k], "_related", strandInfoText)
        ))

        fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = MEAN_FIVE_PRIME_CUT_SITE_DISTANCE,
                                        strandAlign = bool),
               sep = '\t', na = "NA", file = generateFilePath(
          featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = FIVE_PRIME,
          cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
          timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
          additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k], "_related", strandInfoText)
        ))

      }
    }
  }
}
```

### 2023-11-27 R/NHF1_FeatureRelativeFigureGeneration.Rmd
Added analysis with updated nucleosome map
- The previous nucleosome map (hg19_mnase_all) was not well documented. The new nucleosome map (hg19_LCL_mnase_all_mappable) has much clearer documentation on its origins.
- This new map also has blacklisted regions removed, using Dr. Wyrick's intersect_MNasenucs_Blacklist.pl script and the DAC_Duke_hg19_excludable regions, which were also added to the new "perl" directory.
- R scripts were also altered slightly to remove whitespace, standardize spacing after commas, etc.
- Lastly, a bug was discovered and fixed in the figure S16 generation code. (5'

---
title: "NHF1_FeatureRelativeFigureGeneration"
author: "Ben Morledge-Hampton"
date: "2023-07-13"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered, TG_filtered]
---

@@

cellType = "NHF1"
CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
mismatchTypes = list(`C>T_CC>TT` = NULL)
TFBSs = list(`CTCF_known1_DHS` = NULL, `CTCF_known1_non-DHS` = NULL)
nucMaps = list(`hg19_mnase_all` = NULL)

@@

opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, 
               fig.path = paste0(file.path("deamination_analysis_output",cellType,
                                           paste(c(filtering,"feature_relative_figures"), collapse = '_')),
                                 .Platform$file.sep))

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", cellType)
featureRelativeDataDirectory = file.path(deaminationDataDirectory,"feature_relative_analysis")
```

@@

      featureRelativePositionData = fread(generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativePositionCounts, ".tsv",
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(tfbs,"_related")
      ))

      meanThreePrimeCutSiteDistanceData = fread(generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = THREE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(tfbs,"_related")
      ))

      meanFivePrimeCutSiteDistanceData = fread(generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = FIVE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(tfbs,"_related")
      ))

      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION,
                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"))

      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION, meanThreePrimeCutSiteDistanceData,
                                THREE_PRIME, title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"))

      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION, meanFivePrimeCutSiteDistanceData,
                                FIVE_PRIME, title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"))

@@

      featureRelativePositionData = fread(generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativePositionCounts, ".tsv",
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(nucMap,"_related")
      ))

      meanThreePrimeCutSiteDistanceData = fread(generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = THREE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(nucMap,"_related")
      ))

      meanFivePrimeCutSiteDistanceData = fread(generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = FIVE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(nucMap,"_related")
      ))

      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION,
                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"))

      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION, meanThreePrimeCutSiteDistanceData,
                                THREE_PRIME, title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"))

      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION, meanFivePrimeCutSiteDistanceData,
                                FIVE_PRIME, title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"))

@@

        meanThreePrimeCutSiteDistanceData = fread(generateFilePath(
          featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = THREE_PRIME,
          cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
          timepoint = CPDTimepoint, includedMismatches = mismatchType,
          additionalInformation = paste0(nucMap,"_related")
        ))

        meanFivePrimeCutSiteDistanceData = fread(generateFilePath(
          featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = FIVE_PRIME,
          cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
          timepoint = CPDTimepoint, includedMismatches = mismatchType,
          additionalInformation = paste0(nucMap,"_related")
        ))

@@

        print("Mean 3` cut site distance:")
        periodAndSNR = getPeakPeriodicityAndSNR(
          meanThreePrimeCutSiteDistanceData[order(Feature_Relative_Mismatch_Pos)][abs(Feature_Relative_Mismatch_Pos) <= 60,
                                                                                  Mean_Three_Prime_Cut_Site_Distance], 5, 25)
        print(paste("  Peak Period:",periodAndSNR[1]))
        print(paste("  SNR:",periodAndSNR[2]))

        print("Mean 5` cut site distance:")
        periodAndSNR = getPeakPeriodicityAndSNR(
          meanFivePrimeCutSiteDistanceData[order(Feature_Relative_Mismatch_Pos)][abs(Feature_Relative_Mismatch_Pos) <= 60,
                                                                                  Mean_Five_Prime_Cut_Site_Distance], 5, 25)
        print(paste("  Peak Period:",periodAndSNR[1]))
        print(paste("  SNR:",periodAndSNR[2]))
        print("")

@@

>>>>

---
title: "NHF1_FeatureRelativeFigureGeneration"
author: "Ben Morledge-Hampton"
date: "2023-07-13"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: ~/bioinformatics
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects, ~/bioinformatics]
  filtering:
    label: "Filtering"
    value: TGG_filtered
    input: select
    choices: [NONE, TGG_filtered, TG_filtered]
---

@@

cellType = "NHF1"
CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
mismatchTypes = list(`C>T` = NULL, `CC>TT` = NULL, `C>T_CC>TT` = NULL)
TFBSs = list(`CTCF_known1_DHS` = NULL, `CTCF_known1_non-DHS` = NULL)
nucMaps = list(`hg19_mnase_all` = NULL, `hg19_LCL_mnase_all` = NULL, `hg19_LCL_mnase_all_mappable` = NULL)

@@

opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5,
               fig.path = paste0(file.path("deamination_analysis_output", cellType,
                                           paste(c(filtering, "feature_relative_figures"), collapse = '_')),
                                 .Platform$file.sep))

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", cellType)
featureRelativeDataDirectory = file.path(deaminationDataDirectory, "feature_relative_analysis")
```

@@

      featureRelativePositionData = fread(generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativePositionCounts, ".tsv",
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(tfbs, "_related_strand_aligned")
      ))

      meanThreePrimeCutSiteDistanceData = fread(generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = THREE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(tfbs, "_related_strand_aligned")
      ))

      meanFivePrimeCutSiteDistanceData = fread(generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = FIVE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(tfbs, "_related_strand_aligned")
      ))

      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION,
                                plotCountsMirror = TRUE, smoothCountsData = FALSE, mainYAxisLabel = "C>T Mismatches",
                                countsPlotColor = "black", countsMirrorColor = "gold2",
                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"),
                                xAxisLabel = "TFBS-Relative Position")

      plotFeatureRelativeCounts(meanThreePrimeCutSiteDistanceData, FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                                smoothCountsData = FALSE, countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                                meanCutSiteDistanceTable = meanFivePrimeCutSiteDistanceData,
                                cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"),
                                xAxisLabel = "TFBS-Relative Position")

@@

      featureRelativePositionData = fread(generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativePositionCounts, ".tsv",
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(nucMap, "_related_strand_aligned")
      ))

      meanThreePrimeCutSiteDistanceData = fread(generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = THREE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(nucMap, "_related_strand_aligned")
      ))

      meanFivePrimeCutSiteDistanceData = fread(generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = FIVE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(nucMap, "_related_strand_aligned")
      ))

      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION,
                                plotCountsMirror = TRUE, smoothCountsData = FALSE, mainYAxisLabel = "C>T Mismatches",
                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"),
                                xAxisLabel = "Dyad-Relative Position", xlim = c(0, 300))

      plotFeatureRelativeCounts(meanThreePrimeCutSiteDistanceData, FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                                smoothCountsData = FALSE, countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                                meanCutSiteDistanceTable = meanFivePrimeCutSiteDistanceData,
                                cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"),
                                xAxisLabel = "Dyad-Relative Position", xlim = c(-100, 100))

      plotFeatureRelativeCounts(meanThreePrimeCutSiteDistanceData, FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                                smoothCountsData = FALSE, countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                                meanCutSiteDistanceTable = meanFivePrimeCutSiteDistanceData,
                                cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"),
                                xAxisLabel = "Dyad-Relative Position", xlim = c(0, 300))

@@

        meanThreePrimeCutSiteDistanceData = fread(generateFilePath(
          featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = THREE_PRIME,
          cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
          timepoint = CPDTimepoint, includedMismatches = mismatchType,
          additionalInformation = paste0(nucMap, "_related")
        ))

        meanFivePrimeCutSiteDistanceData = fread(generateFilePath(
          featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = FIVE_PRIME,
          cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
          timepoint = CPDTimepoint, includedMismatches = mismatchType,
          additionalInformation = paste0(nucMap, "_related")
        ))

@@

        print("Mean 3` cut site distance:")
        periodAndSNR = getPeakPeriodicityAndSNR(
          meanThreePrimeCutSiteDistanceData[order(Feature_Relative_Mismatch_Pos)][abs(Feature_Relative_Mismatch_Pos) <= 60,
                                                                                  Mean_Three_Prime_Cut_Site_Distance], 5, 25)
        print(paste("  Peak Period:", periodAndSNR[1]))
        print(paste("  SNR:", periodAndSNR[2]))

        print("Mean 5` cut site distance:")
        periodAndSNR = getPeakPeriodicityAndSNR(
          meanFivePrimeCutSiteDistanceData[order(Feature_Relative_Mismatch_Pos)][abs(Feature_Relative_Mismatch_Pos) <= 60,
                                                                                  Mean_Five_Prime_Cut_Site_Distance], 5, 25)
        print(paste("  Peak Period:", periodAndSNR[1]))
        print(paste("  SNR:", periodAndSNR[2]))
        print("")

@@

```{r linker_region_periodicity_analysis}
library(mutperiodR)

        meanThreePrimeCutSiteDistanceData = fread(generateFilePath(
          featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = THREE_PRIME,
          cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
          timepoint = CPDTimepoint, includedMismatches = mismatchType,
          additionalInformation = paste0(nucMap, "_related")
        ))

        meanFivePrimeCutSiteDistanceData = fread(generateFilePath(
          featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = FIVE_PRIME,
          cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
          timepoint = CPDTimepoint, includedMismatches = mismatchType,
          additionalInformation = paste0(nucMap, "_related")
        ))

        print("Mean 3` cut site distance:")
        print("  pre-linker:")
        periodAndSNR = getPeakPeriodicityAndSNR(
          meanThreePrimeCutSiteDistanceData[
            Feature_Relative_Mismatch_Pos < -70 & Feature_Relative_Mismatch_Pos > -120,
            Mean_Three_Prime_Cut_Site_Distance], 5, 25)
        print(paste("    Peak Period:", periodAndSNR[1]))
        print(paste("    SNR:", periodAndSNR[2]))

        print("  post-linker:")
        periodAndSNR = getPeakPeriodicityAndSNR(
          meanThreePrimeCutSiteDistanceData[
            Feature_Relative_Mismatch_Pos > 70 & Feature_Relative_Mismatch_Pos < 120,
            Mean_Three_Prime_Cut_Site_Distance], 5, 25)
        print(paste("    Peak Period:", periodAndSNR[1]))
        print(paste("    SNR:", periodAndSNR[2]))

        print("Mean 5` cut site distance:")
        print("  pre-linker:")
        periodAndSNR = getPeakPeriodicityAndSNR(
          meanFivePrimeCutSiteDistanceData[
            Feature_Relative_Mismatch_Pos < -70 & Feature_Relative_Mismatch_Pos > -120,
            Mean_Five_Prime_Cut_Site_Distance], 5, 25)
        print(paste("    Peak Period:", periodAndSNR[1]))
        print(paste("    SNR:", periodAndSNR[2]))

        print("  post-linker:")
        periodAndSNR = getPeakPeriodicityAndSNR(
          meanFivePrimeCutSiteDistanceData[
            Feature_Relative_Mismatch_Pos > 70 & Feature_Relative_Mismatch_Pos < 120,
            Mean_Five_Prime_Cut_Site_Distance], 5, 25)
        print(paste("    Peak Period:", periodAndSNR[1]))
        print(paste("    SNR:", periodAndSNR[2]))

        print('')
    }
  }
}
```
